TRITON: Globally Consistent Sim-to-Real Transfer ``I can't believe it's not real!"

### 2022-06-10 CORL/example.tex
Added better intro to the neural texture section

\subsection{Neural Texture}

@@

	TODO: Put summary of section here; don't strart with 'b is the batch size'

	$B$ is the batch size. Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.

>>>>

\subsection{Neural Texture and Projection}

@@

	TRITON's neural texture module is what lets it learn the albedo of objects, and thus take advantage of 3d geometric priors. By learning this texture, we can encode features directly onto the surfaces of the 3d objects in a scene, which the image translation module uses to maintain visual consistency between states and viewpoints.

	Given a batch of $B$ UVL Scenes $s_{1\dots B}$ with $L$ different label values, we project $L$ different neural textures $\tau_{1\dots L}$ onto that scene; obtaining projections $\tau_{1\dots B}$. This projection mechanism is illustrated in figure \ref{fig:uvl_explanation}.
